A decentralized network support middleware for MMOGs

### 2009-09-09 textos/PlanoDoutorado/Lugano/short_planodoc_lugano.tex

The purpose of this study plan is, therefore, to develop an innovative solution with a decentralized approach. More specifically, it is intended to use a decentralized overlay network such as those used for resource sharing -- e.g. Pastry \cite{rowstron2001psd}, Tapestry \cite{zhao2004trg}, Koord \cite{kaashoek2003ksd} and others -- to create a geographically distributed system composed of low-cost volunteer nodes. This system will then act as a geographically distributed server to which the players connect via a gateway. Obviously, this model brings several questions, which were trivial to solve when using the traditional server architecture, but that become much more complex in a geographically distributed server scenario, such as: state consistency among the server nodes; coordination of entry, exit and crash of some of them, in order to keep the service available as much as possible; distributed persistence; optimal management of the scarce resources of the server system; and so on.

@@

>>>>

The purpose of this study plan is, therefore, to develop an innovative solution with a decentralized approach. More specifically, it is intended to create a middleware which uses a decentralized overlay network such as those used for resource sharing -- e.g. Pastry \cite{rowstron2001psd}, Tapestry \cite{zhao2004trg}, Koord \cite{kaashoek2003ksd} and others -- to create a geographically distributed system composed of low-cost volunteer nodes. This system will then act as a geographically distributed server to which the players connect via a gateway. Obviously, this model brings several questions, which were trivial to solve when using the traditional server architecture, but that become much more complex in a geographically distributed server scenario, such as: state consistency among the server nodes; coordination of entry, exit and crash of some of them, in order to keep the service available as much as possible; distributed persistence; optimal management of the scarce resources of the server system; and so on.

@@

To achieve the goals outlined for the research project, a schedule has been designed, considering a nine-month academic year. This period has been chosen to fit the length of the scholarship to which this application refers. In Switzerland, it is intended to execute some of the essencial parts of the research project designed for a Ph.D. course in UFRGS (Brazil). This project will, therefore, result in an international cooperation between both UFRGS and the Swiss university. The tasks to be performed in Switzerland are:

\begin{enumerate}

  \item Detailed definition of the services to be provided by the MMOG decentralized support middleware, which are, mainly:

    \begin{enumerate}
      \item Develop an algorithm or technique to manage the consistency of the game world simulation among the server nodes of the system;

      \item Design Store and retrieve the persistent state of the game in a distributed manner, using replication and providing reliability, while 
    \end{enumerate}

  \item Research and development of innovative solutions to deliver these services, considering the needs of MMOGs;

  \item Create a prototype which implements these services;

  \item Validate the proposed middleware by simulating a game on the developed prototype.

\end{enumerate}

%todas as etapas irão gerar produções bibliográficas
